---
output:
  flexdashboard::flex_dashboard: default
  html_document: default
runtime: shiny
---
title: "R Package Download Information"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: scroll
    source_code: embed  
runtime: shiny
---


```{r setup, include=FALSE}
library(shiny)
library(flexdashboard)
# Libraries required are being loaded here


library(miniCRAN)
library(pkgsearch)
library(cranlogs)
library(packageRank)

```




### Details & Description of Package

```{r}
textInput("package_selected", "Please Enter Package Name", "ggplot2")
renderPrint(packageDescription(input$package_selected))
```



### Date wise Spiky Graph of Downloads - Please Select Date Range

```{r}
textInput("from", "From", "2020-01-01")
textInput("to", "To", "2020-12-31")
renderPlot(plot(cranDownloads(packages = input$package_selected, from = input$from, to = input$to),
       r.version = TRUE))
```


### Date wise Table of Download Details 

```{r}
renderPrint(cranDownloads(packages = input$package_selected, from = input$from, to = input$to))
```


Authors {data-orientation=rows}
=====================================   
### Once user enters the name of the package, the dashboard will show its description, and further by mentioning the date range it will show a spiky graph of downloads for a given date range followed by a table with details of downloads. This dashboard is highly beneficial for a data scientist, R package maintainers, and other R users to get information about R package and downloads at one point. It is also helpful to undersatnd the usage freqency and popularity of the package.
